\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.20\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Paulus Hermanto} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(425) 835-6592 \\ Lincoln, NE} 
\address{\href{mailto:paulus.hermanto@huskers.unl.edu}{paulus.hermanto@huskers.unl.edu} \\ \href{https://linkedin.com/paulus-hermanto}{linkedin.com/paulus-hermanto}}

\begin{document}
\begin{rSection}{OBJECTIVE}
{Graduate student pursuing a Masters Degree in Statistics seeking an internship role in a related area.}

\end{rSection}

\begin{rSection}{Education}
{\bf Master of Statistics}, University of Nebraska-Lincoln \hfill {Expected 2024}\\
Relevant Coursework: Computing Tools for Statisticians, Design of Experiments, Probability Theory.

{\bf Actuarial Exams Passed: P, FM}

{\bf Bachelor of Actuarial Science w/ Minor in Mathematics}, University of Nebraska-Lincoln \hfill {2017 - 2019}
\end{rSection}

\begin{rSection}{SKILLS}

\begin{tabular}{@{}>{\bfseries}l @{\hspace{6ex}} l}

Technical Skills & Microsoft Office (Word, Excel, Powerpoint, Access), R, SAS.\\
Other Skills & Bahasa Indonesia.\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}
\textbf{Graduate Teaching Assistant} \hfill Aug 2022 - Current\\
University of Nebraska-Lincoln \hfill \textit{Lincoln, NE}
 \begin{itemize}
    \itemsep -1pt {} 
     \item Teaching introductory course – STAT 218 (practical application of statistical thinking to contemporary issues; collection and organization of data; probability distributions; statistical inference; estimation; and hypothesis testing).
     \item Grading quizzes and exams of students in STAT 218.
    \item Conducting office hours for to provide additional support for students and allow students to ask questions.
 \end{itemize}
\textbf{UI/BPCU Adjudicator} \hfill Nov 2020 - Jul 2022\\
 State of Nebraska - Department of Labor \hfill \textit{Lincoln, NE}
 \begin{itemize}
    \itemsep -1pt {} 
     \item Participating in various projects for the department, such as: employer charging project, vital statistics, appeal hearings, and investigating potential fraud cases to maintain the integrity of the Unemployment insurance Program in the state of NE.
     \item Performing wage audits and assessing amounts of overpayments to ensure the accuracy in benefits going out to claimants.
    \item Analyzing benefit claims to obtain the necessary information to write legal formal determinations of benefit eligibility.
 \end{itemize}
 \textbf{Actuarial Technician} \hfill Aug 2020 - Oct 2020\\
 Transamerica \hfill \textit{Cedar Rapids, IA / Remote}
 \begin{itemize}
    \itemsep -1pt {} 
     \item Preparing and analyzing statistical reports of data to be used by the actuarial staff using MS Access, Excel, Axis and MoSes.
     \item Providing quantitative support in financial analysis, management reporting, modeling and other actuarial research.
    \item Running Macros and queries as needed by the department.
 \end{itemize}
 
\end{rSection} 

\begin{rSection}{Some Achievements \& Extra-Curricular Activities} 

\begin{tabular}{@{\hspace{6ex}} l }
Edmonds CC ISS Scholarship Award, George Beadle Scholarship, Phi Theta Kappa Honor Society,\\
College of Arts \& Sciences Scholarship - Sallie W. Nixon Fund, Yamaha Piano Grade Level 10\\
\end{tabular}

\end{rSection}

\end{document}
